% Created 2016-03-23 Wed 11:52
\documentclass[10pt]{leaflet}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
%\author{Lisa Siebel}

\date{\vspace{-5ex}}
\title{Guidelines for respectful conduct  at the GPN}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle

Hello and welcome to the Gulaschprogrammiernacht, a event of
technology, yummy food and lots of great people. The following hints
are a guideline to dealing with those people in order to avoid
conflict and to ensure a great GPN for everybody.



\section{General}
\label{sec-1}
\begin{itemize}
\item Try to treat others the way you would want to be treated
\item If you're unsure, ask politely
\item If someone is mean, try to talk
\item If things turn ugly or you need help, please contact our team.
  We wear green badges and can be reached by Dectphone, number 113. There
  are photos of us on the info desk.
\end{itemize}


\subsection{First impression}
\label{sec-1-1}
Wow, there's lots of people here...\\
\emph{Yep, last year there where about 500 and the GPN continues to grow}\\\\

Are all of those people nerds?\\
\emph{Some are just here to get a look. Maybe some of them are nerds that don't know yet that they are ;-)}\\\\

OK, but how about \ledots{}?\\
\emph{You'll find information on specific groups in this flyer. Read on...}

\section{Girls and Women}
\label{sec-2}
Wow, there a girls here? Are they someones girlfriend? If not, can I
hit on them? I could use a girlfriend\ldots{}

\emph{Sadly, the amount of girls and women in technical professions is
  low. A lot of them think it's an environment hostile to them and
  won't stay long. Please don't be part of the reason.}
\subsection{Do's}
\label{sec-2-1}
\begin{itemize}
\item Treat girls and women with respect and politeness. Many of them
  have already made bad experiences at chaos events.
\item Ask them about their projects, hack-spaces, interests -- like
  everyone else.
\end{itemize}
\subsection{Don'ts}
\label{sec-2-2}
\begin{itemize}
\item This might sound strange, but being hit on can be
  annoying. Especially on an event with lots of guys who all have that
  same idea. If the situation isn't clearly a flirty one, just don't
  do it, you'll ruin her day.
\item Just as bad: Being constantly reduced to the girl role: ``Are
  you here with your boyfriend?'' ``What does a girl do here?''
  etc. It hurts to have ones tech skills doubted like that by your
  peers and it frustrates lots of young hacker girls.
\item On the other hand it's annoying to have to act like a guy and to
  feel that you can't really speak out against disgusting, disturbing
  or sexist talk without losing your status as the cool girl. Please
  be polite.
%\item Nicht jede von uns ist Feministin, Expertin für Frauenprobleme
 % oder eine Koryphäe des Sozialen. Es ist ätzend, sich für andere
 % Frauen rechtfertigen oder sie erklären zu müssen, und den modernen
  %Feminismus gegen wikipediaerfahrenen Rethoriker verteidigen zu
  %sollen. Wir sind zum Hacken und für nette Leute hier, lasst den
  %anderen Kram in Ruhe, außer wir zeigen deutliches Interesse daran.
\end{itemize}

\subsection{If you're female and are stressed by the guys}
Talk to us or give us a call. We have some girls in our team and we
won't tolerate sexism.\\ \\


\section{Neurodivergents}
\label{sec-3}
Some people here seem \ldots{} a bit strange. They look away when
talking, snap their fingers or shake and seem to enjoy that a
lot. Somehow I can't really connect with them. What's wrong?


\emph{Neurodivergence isn't fully understood. Many neurodivergents
  suffer from the fact that neurotypical people can't really relate to
  them or reduce them to stereotypes. However, everyone could profit
  from different perspectives.}

\subsection{Do's}
\label{sec-3-1}
\begin{itemize}
\item Neurodivergents are also here to have fun with technology and to
  meet nice people. Treat them in a way that they can feel as a part
  of the whole, without being paternalistic.
\item If you want to ask about something, ask politely, that makes it
  much easier to answer. 
\end{itemize}

\subsection{Don'ts}
\label{sec-3-2}
\begin{itemize}
\item No one likes being reduced to one aspect of their live. Allow
  people to be persons instead of reducing them to being ``other''.
  Don't invalidate their anger at being treated badly.
\item Don't insist on behavior typical of people with autism or
  Asperger, even if you know people who are like that.
\item Diagnoses are a really touchy subject. No one needs a doctor's
  permission to be different and often the medical establishments does
  a lot of damage too.
\end{itemize}

\subsection{If you're neurodivergent and have trouble with the neurotypicals}
Come to us or call us, we have some experience with the topic and can
help you.\\ \\

\section{Trans* \& Queer}
\label{sec-5}
I'm not sure whether some people here are male or female -- and some
look one way but wear those pronoun badges that say another thing. Oh
and some of them are obviously in love with one another. That's all
just for fun, right?

\emph{Gender and Sexuality are socially constructed and are under
  increased scrutiny. More and more people dare to live as the
  other, a third, without or with a fluid and changing gender. Some
  experiment. And of course, all sorts of people fall in love with one
  another.}
\subsection{Do's}
\label{sec-5-1}
\begin{itemize}
\item Respect pronouns, names and identities. No one is obligated to
  prove anything to you. Try to ask what pronoun to use instead of
  guessing. Sometimes the name can give a hint. If you really can't
  deal, leave those people alone and think about it.
\item Likewise, please respect other sexualities: If you aren't into
  someone for any reasons, tell them and leave it at that. Don't try
  to ``convert'' people.
\end{itemize}
\subsection{Don'ts}
\label{sec-5-2}
\begin{itemize}
\item Please don't hurt people with stereotypes. The TV lies, so does
  YouTube.
\item Please don't explain to people what toilets they can and can't
  use. If there's any problem (like guys abusing those guidelines to
  harass girls and women), call us or the organizers.
\end{itemize}
\subsection{If you're trans* or queer (or think you might be)}
Just get in touch, we love to help. If you have any questions or just
want to talk to someone, ask our queer non-binary demi-femme, Lisa/lyzz.
\clearpage



\section{Foreigners, People of Color, people with an migrant background}

\label{sec-4}
Hey, there's people here who look like they are from far away? Can I
explain to them what Germany is like?

\emph{Modern migration leads to diversity in origins, nerds
  included. Those who come to the GPN are here to meet nice people and
  play with fascinating technology. Communication can be difficult
  sometimes. Luckily, most nerds are cosmopolitans and both sides
  benefit from that.}

\subsection{Do's}
\label{sec-4-1}
\begin{itemize}
\item Be nice and maybe help in translation. Often clear messages are
  better than highly elaborated and gramatically perfect language.
\end{itemize}
\subsection{Don'ts}
\label{sec-4-2}
\begin{itemize}
\item Stereotypes (including positive ones) can be hurtfull. Be
  mindful and spare people those.
\item Looks don't predict someones origin or home. Try talking German
  first instead of making people feel like they are strangers.
\end{itemize}
\subsection{Wenn du selbst einen Migrationshintergrund hast, oder POC bist  und  Hilfe brauchst / If you are a POC or a migrant and want help}
Ruf uns einfach an, wir helfen dir. Just give us a call, we will help
you.\\ \\ \\ \\  \\ \\ \\ \\ \\


\section{Children}
\label{sec-6}
Gosh, there are tiny people here! Did the get lost?

\emph{Some hackers start really young and the GPN attracts people of
  all ages. Projects like ``Chaos macht Schule'' try to educate
  the youngsters in media literacy.}

\subsection{Do's}
\label{sec-6-1}
\begin{itemize}
\item You're older, be a paragon.
\item If the youth is curious about your project, please explain
  it. Use age appropriate language and repeat important
  information. Don't take it personal if the kids shrug and move on.
\item You probably remember being a kid. What would you want a
  grown-up to be like? Would that be sensible? If yes, be that person.
\end{itemize}


\subsection{Don'ts}
\label{sec-6-2}
\begin{itemize}
\item Please don't be a meanie. If you need silence, say so
  politely. Children have feelings too.
\item Please don't quarrel with the kiddies. Just call us, we can handle it.
\end{itemize}
\subsection{If you're a youngster and need help}
Come to us (the folks with the green badges) or call us on our Dectphone (113).


\section{Those rules suck! You're not the boss of me! What would happen if I where to spite you by spraying the following subversive art on the walls of the ZKM: A huge, neon-flourescent, anatomically correct\ldots{}}

\label{sec-7}
Make my day, punk. Seriously though, we regret having to have
guidelines but sadly the GPN has grown to large to just assume the
usual hackers code. Thus we make the rules explicit beforehand. If you
want to argue, come by or call. Best to ask for Lisa/lyzz, she's
responsible for this flyer anyhow.
\end{document}
